The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-01-09 analysis/paper/paper.qmd
adapted text cleaning
Update papeer metadata

---
title: "Title Goes Here"
author:
  - Jane Doe:
      correspondence: "yes"
      email: janedoe@fosg.org
      orcid: 0000-0003-1689-0557
      institute:
        - fosg
        - fop
  - John Q. Doe:
      institute: fosg
      orcid: 0000-0003-1689-0558
  - Peder Ås:
      institute: fosg
      orcid: 0000-0003-1689-0559
  - Juan Pérez:
      orcid: 0000-0003-1689-0551
      institute:
        - name: Acme Corporation
  - Max Mustermann:
      orcid: 0000-0003-1689-0552
institute:
  - fosg:
      name: Formatting Open Science Group
      address: 23 Science Street, Eureka, Mississippi, USA
  - fop: Federation of Planets
title-block-published: "Last updated"  
date: now
date-format: long
format: 
  docx:
    reference-doc: "../templates/template.docx" # Insert path for the DOCX file
execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->

@@

```{r}
#| label: setup
library(dplyr)
library(readr)
devtools::load_all(".")

# read csv file with pages that are useful for the analysis
emu_theses <- read_csv(here::here("analysis","data", "raw_data", "emu-theses.csv")) %>%
  mutate(pdf_filename = paste0(year, "-", author_surname, ".pdf")) %>%
  mutate(text = "")

pdf_paths<- here::here("analysis","data", "raw_data", emu_theses$pdf_filename)

emu_theses$text <- convert_pdf_text(pdf_paths)

```

@@

Here is a citation [@Marwick2017]

# Background

@@

@@

>>>>

---
title: "The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach"
author:
  - Jane Doe:
      correspondence: "yes"
      email: janedoe@fosg.org
      orcid: 0000-0003-1689-0557
      institute: tud
  - John Q. Doe:
      email: johndoe@fosg.org
      orcid: 0000-0003-1689-0558
      institute: tud
institute:
  - tud:
      name: Delft University of Technology
      address: Julianalaan 134, 2628 BL, Delft, Zuid-Holland, The Netherlands
title-block-published: "Last updated"  
date: now
date-format: long
format: 
  docx:
    reference-doc: "../templates/template.docx" # Insert path for the DOCX file
execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  urbanism; education; post-master; text mining
highlights: |
  These are the highlights. 
---

@@

```{r}
#| label: setup
#| echo: false
library(tidyverse)
library(tmap)
```

@@

The research presented in this paper was prompted by the closure of the European post-Master of Urbanism (EMU) of the Department of Urbanism at the Faculty of Architecture and the Built Environment, TU Delft. 
<!-- Complete paragraph about the program -->

In order to describe the legacy of the EMU program, including the distinctive features of the didactics employed in it, this paper aims to reveal the main topics taught in it and how those topics had evolved through the years of the program. To that end, we employed a text mining approach in which we analysed its output: 97 theses of 100+ pages each produced over the years for the entire duration of the program between 2007-2021.

@@

## Data collection
The theses are available in PDF format with complex layouts typical to an urbanism project in which text and various types of graphics are combined.

## Data analysis

[@silge2017a]
[@hvitfeldt2021a]

@@

```{r}
#| label: map-theses
#| warning: false

# Create dummy data
location_names <- as.data.frame(c("Paris, France", "Bucharest, Romania", "Delft, The Netherlands"))

# Geocode

# Visualise thesis locations on world map
world <- map_data("world")
ggplot() +
  geom_map(
    data = world, map = world,
    aes(long, lat, map_id = region),
    color = "black", fill = "lightgray", size = 0.1
  )
```
